Personality and political beliefs across the lifespan

### 2019-12-01 scripts/manuscript.Rmd
added heatmap

```{r setup, include = FALSE}
library(papaja)
library(rio)
library(here)
library(tidyverse)
library(psych)
library(knitr)
library(MBESS)

@@

untidy_cor <- untidy %>% 
  select(-c(1:6)) %>% 
  rename('Social conservatism' = 'social_conservatism',
         'Economic conservatism' = 'economic_conservatism',
         'Openness to experiences' = 'openness_to_experiences',
         'Emotional stability' = 'emotional_stability')
cor_conservatism_ocean <- round(cor(untidy_cor),2)
upper_s<-cor_conservatism_ocean
upper_s[upper.tri(cor_conservatism_ocean)]<-""
upper_s<-as.data.frame(upper_s) %>%
  apa_table(
    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
  landscape = TRUE,
  font_size = "tiny")
```

```{r correlations heatmap, include = FALSE}

```{r figure1}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
       color = "Personality Trait")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~conservatism_type)
```

@@

<div id = "refs"></div>
\endgroup

>>>>

```{r setup, include = FALSE}
library(papaja)
library(rio)
library(here)
library(tidyverse)
library(psych)
library(knitr)
library(MBESS)
library(viridis)

@@

@@

<div id = "refs"></div>

untidy_cor <- untidy %>% 
  select(-c(1:6)) %>% 
  rename('Social conservatism' = 'social_conservatism',
         'Economic conservatism' = 'economic_conservatism',
         'Openness to experiences' = 'openness_to_experiences',
         'Emotional stability' = 'emotional_stability')
cor_conservatism_ocean <- round(cor(untidy_cor),2)
upper_s<-cor_conservatism_ocean
upper_s[upper.tri(cor_conservatism_ocean)]<-""
upper_s<-as.data.frame(upper_s) %>%
  apa_table(
    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
  landscape = TRUE,
  font_size = "tiny")

heatmap(cor_conservatism_ocean,
        Rowv = NA,
        Colv = NA,
        main = "Correlation Heatmap",
        margins = c(15,15),
        col = viridis(100, direction = -1))
```

```{r figure1, fig.cap= ""}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
       color = "Personality Trait")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~conservatism_type)
```

\endgroup
